% LaTeX file for resume 
% This file uses the resume document class (res.cls)

% FIXME: REWRITE EVERYTHING BEFORE EVEN TRYING TO SUBMIT IT AGAIN!!!!!!

\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\topmargin=-0.5in  % start text higher on the page
\setlength{\textheight}{10in} % increase text height to fit resume on 1 page
\begin{document}  
\name{Massimo Gengarelli}
\address{Curriculum Vitae}
                           
\begin{resume}                        
 
\section{Personal Informations}
	\begin{ncolumn}{2}
		\underline{First name}:     & Massimo                                 \\
		\underline{Last name}:      & GENGARELLI                              \\
		\underline{Residence}:      & 1260 av. J. Grec, 06600 Antibes, FRANCE \\
		\underline{Born}:           & April 6th, 1986                         \\
		\underline{Marital status}:	& P.A.C.S.                                \\
		\underline{Phone Number}:   & +33 (0)6 43 87 57 67                    \\
		\underline{Email}:          & massimo.gengarelli@gmail.com 
	\end{ncolumn}


\section{Education}       
\underline{Universit\`a degli studi ``Alma Mater Studiorum'' di Bologna} \\
Bachelor of Science degree in \textbf{Computer Science}                  \\
(Final Mark: 105/110, Avg Mark: 27/30)                                   \\
Thesis: ``ShockVM: design and realization of an heterogeneous cluster of
virtual machines interfaced to a Web Application'' 
\vspace{3 mm}

\renewcommand{\labelitemi}{$\rightarrow$}
\section{Working Experiences}
\underline{Alten Consultant for ORANGE} \\

\emph{June 2014} - current \\
As a part of the ``Backfill'' team in Orange's services, we are responsible of developing
and constantly improving the search engine.  The team covers all the technical subjects
from the crawling of websites, indexing, scoring and generating a response's list based on
the query.  We are not covering the front-end part.

\vspace{2mm}

\section{Skills}
	%% \underline{Programming Languages} % TODO: review 
	%% 	\begin{itemize}
	%% 		\item Advanced knowledge of C/C++
	%% 		\item Advanced knowledge of Object-oriented languages (Java, C\#, C++, Python)
	%% 		\item Advanced knowledge of handling complex algorithms for manipulating
	%% 			data structures
	%% 		\item Good knowledge of functional languages (Clojure, Scheme, Elisp)
	%% 		\item Good knowledge of typographic language \TeX (\LaTeX dialect)
	%% 	\end{itemize}
	
	%% \underline{Development Environments} % XXX: Someone cares? 
	%% 	\begin{itemize}
	%% 		\item Advanced knowledge of VI (m) editor (main editor/IDE)
	%% 		\item Advanced knowledge of the Eclipse IDE (CDT)
	%% 		\item Good knowledges of Emacs editor
	%% 		\item Basic knowledge of NetBeans IDE
	%% 		\item Basic knowledge of Microsoft Visual Studio IDE
	%% 	\end{itemize}

	%\underline{Web Development} % XXX: this part might be rewritten as "Other shit" 
		%\begin{itemize}
			%\item Good knowledge of server-side languages (Ruby, PHP)
			%\item Good knowledge of client-side languages (Javascript)
			%\item Good knowledge of mark-up and styling languages (XML, HTML5, CSS3)
			%\item Advanced knowledge of various frameworks for developing rich web applications 
				%(Servlets/Faces, GWT)
		%\end{itemize}

		% TODO: Rewrite this part
	%\underline{Frameworks, libraries and SDK} % Should put something like "EDIFACT EXPERT" 
		%\begin{itemize} % Yeah, I don't think people care about which libraries you've used in your life 
			%\item Advanced knowledge of the ``Google Web Toolkit'' framework
			%\item Advanced knowledge of the Boost libraries for C++
			%\item Good knowledge of Android SDK
			%\item Good knowledge of the Qt framework
			%\item Good knowledge of the GTK+ framework
			%\item Good knowledge of the JDBC subset of classes for Java
			%\item Basic knowledge in developing kernels for embedded devices
		%\end{itemize}

	%\underline{Software Engineering} % Rewrite this part 
		%\begin{itemize}
			%\item Advanced knowledge of the Design Patterns' 
			%\item Good knowledge of the UML language
		%\end{itemize}

		% TODO: What about Haiku, HelenOS?
		% TODO: Seriously, iOS and Android?
	%% \underline{Operating Systems}
	%% 	\begin{itemize}
	%% 		\item Excellent knowledge of UNIX-based operating systems (BSD, GNU/Linux, Darwin/OSX)
	%% 		\item Good knowledge of NT-based operating systems (Windows XP, Vista, 7, Server)
	%% 	\end{itemize}
	
	%\underline{Systems' Administration}
		%\begin{itemize}
			%\item Excellent skills in configuring domestic LANs
			%\item Excellent skills in installing and configuring various services commonly used
			%in clusters (LDAP, DNS, DHCP, NFS, MX, \ldots)
			%\item Good skills in configuring complex enterprise networks (VPNs, bridging, \ldots)
		%\end{itemize}

		% TODO: rewrite this part using another format.
\section{Languages} 
\underline{Italian}: native. \\
\underline{English}: excellent written and spoken skills. Excellent knowledge of the technical 
IT-related terms. \\
\underline{French}: good written and spoken skills. Good knowledge of the tecnical
IT-related terms.
%% \underline{German}: basic knowledges of the language. \\
 

\section{Professional Experiences}
\underline{Informal Job} \\
I've always been an active member of the opensource community. I have been developing ``amateur''-level
applications for quite a few years now, using different languages (mostly C, C++ and C\#). I currently
own a repository where I store most of my works at http://github.com/massix .

\vspace{2mm}

\underline{From 03/2012 until present} \\
``Alten SAS, consultant for aMaDEUS'' \\
\emph{C++, C and IBM HLASM software development engineer.}
As a part of a small team of development we are responsible of handling the decommissioning of the
old IBM-based platform (TPF) in favor of a distributed one, using opensource technologies running
on Linux kernels. My job mainly consists in handling small projects: starting from the design itself
until the final maintenance, monitoring the load on production environment.

\vspace{2mm}


\underline{From 03/2009 until 10/2009} \\
``Assistenza Informatica Rimini'' \\
System Administrator and Web Developer. I've developed a Web Application to help the customers
in choosing their Workstation-configuration.

\section{Unrelated Seasonal Jobs}
Summer 2006, 2007 and 2008 \\
``Rose \& Crown Pub'' \\
Waiter and barman, mostly night shifts.

\section{Additional Informations}
Particularly good in team-working and handling projects with short deadlines. Excellent
analythical and deductive skills especially when dealing with problems' solving. I'm open-minded
and ready for any kind of job proposal as long as it's coherent and useful to my professional growing. \\
Driving License. \\
\underline{Hobbies and Passions}: programming, computers in general, embedded devices, mathematical and
logical puzzles, chess, soccer and american football.

\section{Availability}
I will be available starting from 3 months after the interview.

\end{resume} 
\end{document}

