% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\topmargin=-0.5in  % start text higher on the page
\setlength{\textheight}{10in} % increase text height to fit resume on 1 page
\begin{document}  
\name{Massimo Gengarelli}

\address{Curriculum Vitae}
                           
                        
\begin{resume}                        
 
\section{Personal Informations}
	\begin{ncolumn}{2}
		\underline{First name}:		& 	Massimo \\
		\underline{Last name}:		& 	Gengarelli \\
		\underline{Residence}:		& 	Via Acquario, 73 -- 47900 Rimini (RN), ITALY \\
		\underline{Born}:			& 	April 6th, 1986 \\
		\underline{Marital status}:	& 	Single \\
		\underline{Phone Number}:	& 	(+39) 338 - 2746525 \\
		\underline{Email}:			& 	massimo.gengarelli@gmail.com 
	\end{ncolumn}


\section{Education}       
From 2006 until 2011 \\
\underline{Universit\`a degli studi ``Alma Mater Studiorum'' di Bologna} \\
Bachelor of Science degree in \textbf{Computer Science} \\
(Final Mark: 105/110, Avg Mark: 27/30) \\
Thesis: ``ShockVM: design and realization of an heterogeneous cluster of
virtual machines interfaced to a Web Application'' 
\vspace{3 mm}

Dal 2001 al 2006 \\
\underline{Istituto Tecnico per il Turismo ``Marco Polo''} \\
Diploma in Tourism (Final Mark: 86/100)
 
\renewcommand{\labelitemi}{$\rightarrow$}
\section{Computers' Skills}
	\underline{Programming Languages}
		\begin{itemize}
			\item Advanced knowledge of procuderal/imperative languages (C)
			\item Advanced knowledge of Object-oriented languages (Java, C\#, C++, Python)
			\item Advanced knowledge of handling complex algorithms for manipulating
				data structures
			\item Good knowledge of functional languages (Scheme, Elisp, Common Lisp)
			\item Good knowledge of typographic language \TeX (\LaTeX dialect)
		\end{itemize}
	
	\underline{Development Environments}
		\begin{itemize}
			\item Advanced knowledge of the Eclipse IDE, used both for Java/J2EE and
				C/C++
			\item Advanced knowledge of Emacs and VI(m) editors
			\item Basic knowledge of NetBeans IDE
			\item Basic knowledge of Microsoft Visual Studio IDE
		\end{itemize}

	\underline{Web Development}
		\begin{itemize}
			\item Good knowledge of server-side languages (Ruby, PHP)
			\item Good knowledge of client-side languages (Javascript)
			\item Good knowledge of mark-up and styling languages (XML, HTML5, CSS3)
			\item Advanced knowledge of various frameworks for developing rich web applications 
				(Servlets/Faces, GWT)
		\end{itemize}

	\underline{Frameworks, libraries and SDK}
		\begin{itemize}
			\item Advanced knowledge of the ``Google Web Toolkit'' framework
			\item Good knowledge of Android SDK
			\item Good knowledge of the Qt framework
			\item Good knowledge of the GTK+ framework
			\item Good knowledge of the JDBC subset of classes for Java
			\item Basic knowledge in developing kernels for embedded devices
			\item Basic knowledge of the Boost libraries for C++
		\end{itemize}

	\underline{Software Engineering}
		\begin{itemize}
			\item Advanced knowledge of the Design Patterns' 
			\item Good knowledge of the UML language
		\end{itemize}

	\underline{Operating Systems}
		\begin{itemize}
			\item Excellent knowledge of UNIX-based operating systems (BSD, GNU/Linux, Darwin/OSX)
			\item Good knowledge of NT-based operating systems (Windows XP, Vista, 7, Server)
		\end{itemize}
	
	\underline{Systems' Administration}
		\begin{itemize}
			\item Excellent skills in configuring domestic LANs
			\item Excellent skills in installing and configuring various services commonly used
			in clusters (LDAP, DNS, DHCP, NFS, MX, \ldots)
			\item Good skills in configuring complex enterprise networks (VPNs, bridging, \ldots)
		\end{itemize}

\section{Foreign Languages} 
\underline{English}: excellent written and spoken skills. Excellent knowledge of the technical 
IT-related terms. \\
\underline{French}: basic knowledges of the language. \\
\underline{German}: basic knowledges of the language. \\
 

\section{Professional Experiences}
\underline{Informal Job} \\
I've always been an active member of the opensource community. I've been developing ``amateur''-level
applications for quite a few years now, using different languages (mostly C, C++ and C\#). I currently
own a repository where I store most of my works at http://github.com/massix . \\
\vspace{2mm}

\underline{From 03/2009 until 10/2009} \\
``Assistenza Informatica Rimini'' \\
System Administrator and Web Developer. I've developed a Web Application to
help the customers in choosing their Workstation-configuration.

\section{Unrelated Seasonal Jobs}
Summer 2006, 2007 and 2008 \\
``Rose \& Crown Pub'' \\
Waiter and barman, mostly night shifts.

\section{Jobs Description}
Following is a short list of some of the softwares I've developed for the opensource
community. 
\begin{itemize}
	\item \underline{Sensitive} $\rightarrow$ http://github.com/massix/Sensitive \\
	Sensitive is a mathematical suite written using \textbf{C++} along with the
	Qt framework and Qwt technical widgets. It is formed up by two softwares
	(Inversitive and Sensitive). The suite is entirely designed using the MVC
	(``Model-View-Controller'') design pattern in order to separate the logic
	of the software from the UI representation of the datas. The sources are
	divided into several directories in order to have a better vision of the
	whole project. The low-level parts of the project are called ``Renal'' and
	``SensitiveProtocol'': the first one is a small library which contains the
	algorithms that are being used to calculate the polynomial interpolations,
	this part uses the ``Template Method'' design pattern in order to retrieve
	the best algorithm for the datas provided by the user; while
	``SensitiveProtocol'' is a library that allows a Sensitive's Client to send
	datas over the network to another Sensitive's Client. The higher-level part
	of the project contains the GUIs, some of the classes are designed using
	the ``Singleton'' Design Pattern in order to avoid memory consumptions (in
	fact, a single instance of the class is kept in memory). The whole suite is
	licensed using the GPL v3+ license.

	\item \underline{libholdem} $\rightarrow$ http://github.com/massix/libholdem \\
	libholdem is a \textbf{C} library I'm developing in order to help other
	developers create their own Poker games. While this is still far from being
	complete, it shows how it's possible to bring the Object-oriented paradigm
	to a programming language that doesn't know how to handle objects. By doing so,
	it will be easy to create wrappers for higher-level languages.
	
	\item \underline{ShockVM} $\rightarrow$ http://github.com/massix/ShockVM \\
	ShockVM (short for: ShockVM is an Heterogeneous Operating Cluster of KVMs
	Virtual Machines) is part of a greater project which involves the creation
	of ``virtually linked'' virtual machines. This part contains a Web
	Interface written entirely in \textbf{Java} using the GWT's framework. The
	application itself allows its users to easily create and use virtual
	machines ``in the cloud'' by using only a full-html5 compliant web browser.
	The users are also free to share their virtual machines with other users of
	ShockVM. The application is actually deployed at the website
	http://forse.v2.cs.unibo.it:8080/LiveVC. The project is licensed using the
	GPL v3+ license.

	\item \underline{VDEPN} $\rightarrow$ http://github.com/massix/vdepn \\
	VDEPN (short for: VDEPN Does Extend Private Networking) is a graphical tool
	written using \textbf{Vala} and the GTK+ framework. It uses the MVC design
	pattern. The tool is intended to be used together with an opensource
	software written by Prof. Renzo Davoli (``vde: virtual distributed
	ethernet'') and helps its users to create their own VPNs.
\end{itemize}

Other softwares may be found at my Github's address (http://github.com/massix),
the softwares presented above are just the ones I'm most proud of.



\section{Additional Informations}
Particularly good in team-working and handling projects with short deadlines.
Excellent analythical and deductive skills especially when dealing with
problems' solving. I'm open-minded and ready for any kind of job proposal as
long as it's coherent and useful to my professional growing. \\
Driving License. \\

\underline{Hobbies and Passions}: programming, computers in general, embedded
devices, mathematical and logical puzzles, chess, soccer and american football.

\section{Availability}
Immediate (except for the time required by an eventual relocation)

\end{resume} 
\end{document}









